
\documentclass[11pt,a4paper,sans]{moderncv}        

\moderncvstyle{banking}                        
\moderncvcolor{blue}                           

\nopagenumbers{}                               


\usepackage[utf8]{inputenc}    
\usepackage{pdfpages}%
\usepackage{multicol}
\usepackage[scale=0.9,top=0.5cm, bottom=0.1cm]{geometry}
\usepackage{xpatch}


\xpatchcmd\cventry{,}{}{}{}

\name{Gregory}{Postnikov}                               

\vspace*{3mm}
\phone[mobile]{+7~(905)~533~8135}                     
\email{postnikov.gyu@phystech.edu}               
\social[github]{Gregory06}   
                 


\begin{document}

\vspace*{-1.05mm}
\makecvtitle
\vspace*{-10mm}

\section{EDUCATION}
\cventry{Moscow, Russia}{}{Moscow Institute of Physics and Technology}{Sep 2017 - Jun 2021}{\hspace*{-2.5 mm} Bachelor's of Science in Applied Math and  Computer Science, 4.6 / 5.0 GPA }{}

%{}{Related Coursework:}
%\vspace{-1.0em}\begin{small}
 %\begin{multicols}{3}
  %  \begin{itemize}
%\item Algorithms and Computational Models
%\item Operation Systems
%\item Compilers Theory
%\item Formal Systems Theory
%\item Computer's Architecture
%\item Graph Theory
%\item Python Language
%\item Deep Learning in NLP problems
%\item Deep Learning in CV problems


%    \end{itemize}
%    \end{multicols}\end{small}    


\section{WORK EXPERIENCE }

\cventry{Moscow, Russia}{}{ABBYY, Inc.}{Feb 2019 - Aug 2019}{\hspace*{-2.5 mm}  Software Engineer Intern}{
NumPy, Pandas, PyTorch, C++, Optimisation on Graph
\begin{itemize}
\item Built a system for evaluating the quality of invoice parsing algorithms that have used by my team daily.
\item Developed invoice's specific part parsing algorithms that outperform existing solutions according to F-measure. 
\item Implemented a new module for clustering invoices, which was added to the production version of ABBYY FlexyCapture.
\end{itemize}}

\cventry{Moscow, Russia}{}{ChefMarket, Inc.}{Jun 2018 - Jul 2018 }{\hspace*{-2.5 mm} Analyst Intern}{
NoSQL, Data Visualisation, Marketing Optimisation
\begin{itemize}
\item Created a marketing data processing system using NoSQL, which automated data collection for marketing team.
\item Built a set of almost 20 demonstrative dashboards using \href{https://www.periscopedata.com/}{\textit{periscopedata.com}} for data visualisation.
\item Analysed advertising spending and saved more than 1.000 \$ by marketing optimisation. 
\end{itemize}}

\section{PROJECTS}

\cventry{}{}{\href{https://github.com/Gregory06/school_timetable_generator}{School Timetable Generator (github)}}{May 2019 }{\hspace*{-2.5 mm} C++ STL, Genetic Optimisation Algorithm }{
\begin{itemize}
\item Developed an algorithm for generating random timetable using backtracking.
\item Built a module that finds an approximation of the best timetable using the ABC algorithm.
\end{itemize}}
% \vspace{1.0em}

\cventry{}{}{\href{https://github.com/Gregory06/MyLittleSell}{Unix Shell Emulator (github)}}{Dec 2018 }{\hspace*{-2.5 mm} C, Unix Operation System}{
\begin{itemize}
\item Developed a parsing module for dividing strings into commands.
\item Implemented a kernel capable of executing most of the real basic Shell commands.
\end{itemize}}

\cventry{}{}{\href{https://github.com/Gregory06/Language}{Programming Language Compiler (github)}}{May 2018 }{\hspace*{-2.5 mm} C, Compilers Theory }{
\begin{itemize}
\item Developed custom "Assembly" language for running simple programs. 
\item Created a translator from the language syntax to "Assembly" using grammars and regular expressions.
\end{itemize}}

\section{EXTRACURRICULAR}
\cventry{Mail.Ru}{PyTorch framework, Convolutional Networks, Modern Networks Architectures}{Deep Learning in CV problems}{Sep 2018 - Dec 2018 }{ }{}
\cventry{iPavlov Lab}{TensorFlow framework, Recurrent Networks, Word2Vec, Modern Networks Architectures}{Deep Learning in NLP problems}{Sep 2017 - May 2018 }{ }{}
\cventry{Mail.Ru}{Basic Concepts, Internal Organization, Asynchrony Basics}{Python Language}{Jul 2018 - Aug 2018 }{ }{}
\cventry{Mail.Ru}{Basic Concepts, Memory Model, Integration with Assembler, C++ Standard Library}{C and C++ Industrial Development}{Sep 2017 - May 2018 }{ }{}

\section{SKILLS}

\begin{itemize}
\item \textbf{Programming:} C, C++, Python, SQL \vspace{0.5em}
\item \textbf{Frameworks:} STL, NumPy, Pandas, PyTorch, TensorFlow \vspace{0.5em}
\item \textbf{Tools:} GIT, SVN \vspace{0.5em}
\item \textbf{Languages:} Russian (native), English (fluent) 
\end{itemize}


% \vspace{1.0em}

\end{document}